---
title: "Group 27 Project"
author: "Jade Butler, Sonia Saxon, Joanna Mendelsohn, Kai Smith"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
library(rmarkdown)
library(BSDA)
library(infer)
library(ggpubr)
library(car)
library(ggplot2)
```

### Problem 1: Read in and Prepare Data

```{r PR}
Fish <- read.csv("fish.csv")
Fish$Site <- factor(Fish$Site)
Fish$AgeP<- factor(Fish$AgeP)
Fish$YrCaught <- factor(Fish$YrCaught)
Fish$YrTagged <- factor(Fish$YrTagged)
count(Fish) 
Fish2 <- filter(Fish, is.na(YrTagged) | YrCaught == YrTagged) 
count(Fish2) 
summary(Fish2) 
``` 



### Problem 3: Exploratory Data Analysis

#### Part 3a) EDAs of Weight, Age and Length

```{r Univariate EDA}
h1 <- ggplot(Fish2, aes(x = AgeP)) +
  geom_bar(fill = "cornflowerblue") + 
  labs(x = "Probable Age (yrs)", 
       title = "A: Fish Measured Age 0-3 Years")  +
  theme_gray(base_size = 9) +
  theme(plot.title = element_text(size = 10))
summary(Fish2$AgeP)
h2 <- ggplot(data = Fish2, aes(x = Length)) + 
  geom_histogram(binwidth = 2, 
                 fill = "cornflowerblue") + 
  labs(title = "B: Captured Fish Measured Fork Length (mm)", 
       x = "Length (mm)") +
  theme_gray(base_size = 9) +
  theme(plot.title = element_text(size = 10))
summary(Fish2$Length)
h3 <- ggplot(data = Fish2, aes(x = Weight)) +
  geom_histogram(binwidth = 2, 
                 fill = "cornflowerblue") + 
  labs(title = "C: Captured Fish Measured Weight (g)", 
       x = "Weight (g)") +
  theme_gray(base_size = 9) +
  theme(plot.title = element_text(size = 10))
summary(Fish2$Weight)
plot <- ggarrange(h1, h2, h3)
annotate_figure(plot, bottom = text_grob("Figure 1 - Univariate Exploratory Data Analysis", face = "bold", ))
```

#### Part 3b) Bivariate EDA of Weight and Length

```{r Bivariate EDA}
s1 <- ggplot(Fish2, aes(x = Length, y = Weight)) +
  geom_point(color="cornflowerblue", 
             size = 1, 
             alpha=.5) +  
  labs(title = "Length on Weight Visualization",
       x = "Weight (g)", 
       y = "Fork Length (mm)" ) +
  theme_gray(base_size = 11) 
annotate_figure(s1, bottom = text_grob("Figure 2 - Bivariate Exploratory Data Analysis", face = "bold", ))
summary(Fish2$Length, Fish2$Weight)
```

### Problem 4: Regression of Weight on Length

#### Part 4a) Natural Log Measured Weight on Measured Fork Length Model

```{r Scatterplot}
s2 <- ggplot(Fish2, aes(x=log(Length), y=log(Weight))) +
  geom_point(color="cornflowerblue", 
             size = 1, 
             alpha=.5) +  
  labs(title = "Natural Log Model of Weight on Length",
       x = "Natural Log Length (mm)", 
       y = "Natural Log Weight (g)") +
  theme_gray(base_size = 9) 
annotate_figure(s2, bottom = text_grob("Figure 3 - Natural Log Measured Weight on Measured Fork Length", face = "bold", ))
```



#### Part 4b) Include Linear Regression

```{r Reg W on L}
s3 <- ggplot(Fish2, aes(x=log(Length), y=log(Weight))) +
  geom_point(color="cornflowerblue", 
             size = 1, 
             alpha=.5) +  
  geom_smooth(method = "lm", se = FALSE, color="black") + 
  labs(x = "Natural Log Fork Length (mm)", 
       y = "Natural Log Weight (g)",
       title = "Natural Log Model with Linear Regression") +
  theme_gray(base_size = 9) 
annotate_figure(s3, bottom = text_grob("Figure 4 - Natural Log Measured Weight on Natural Log Measured Fork Length", 
                                       face = "bold"))
lm1.out <- lm(log(Fish2$Weight) ~ log(Fish2$Length))
  summary(lm1.out)
```
#### Part 4c) Regression Diagnostics

```{r Reg Diagnostics}
par(mfrow = c(2, 2))
par(mar = c(2, 2, 1.5, 1.5))
par(oma = c(2, 2, 2, 2))
plot(Fish2$Weight, Fish2$Length, 
     xlab="Weight (g)", pch=19,
     ylab="Fork Length (mm)", 
     cex.lab=1.25, cex.axis=1.25)

plot(fitted(lm1.out),
     residuals(lm1.out),
     xlab="Fitted Values", 
     ylab="Residuals") 
      abline(h=0, col="blue", lwd=2)

hist(residuals(lm1.out), xlab="Residuals", main = "" )
      
qqnorm(residuals(lm1.out)) 
  qqline(residuals(lm1.out))


mtext(~ bold("Figure 5 - Regression Diagnostics for Natural Log Model"), side = 3, line = -28, outer = TRUE)
```


#### Part 4e) Hypothesis Test for the Regression Slope Parameter

```{r C.I }
t.test(log(Fish2$Weight),log(Fish2$Length), conf.level=0.95)
qt(0.975,2533) 
```


#### Part 4f) Confidence Interval and Prediction Interval for Weight Given Length

```{r CI and PI} 
lm2.out <- lm(log(Weight) ~ log(Length), data=data.frame(Fish2))
new.Length <- data.frame(Length = 70)
(CI.Length70 <- predict(lm2.out, newdata = new.Length, interval = "confidence", level = 0.95))
(PI.Length70 <- predict(lm2.out, newdata = new.Length, interval = "prediction", level = 0.95))
summary(lm2.out)
```


### Problem 5: Fish Fork Length and Site

#### Part 5a) Boxplots of Fish Fork Length by Site

```{r FL by Site}
b1 <- ggplot(Fish2, aes(x = Site, y = Length, fill = Site)) + 
  geom_boxplot() + 
  labs(x = "Site Location", 
       y = "Fork Length (mm)",
       title = "Fish Fork Length by Site") +
  theme_gray(base_size = 11)
annotate_figure(b1, bottom = text_grob("Figure 6 - Boxplot of Fish Fork Length by Site", face = "bold"))
```

#### Part 5b) Inferences for Fish Length

```{r Inference for Length}
site1 <- Fish2 %>%
  filter(Site == "Site 1")
site3 <- Fish2 %>%
  filter(Site == "Site 3")
t.test(site1$Length, site3$Length, conf.level = 0.95)$conf.int
```


#### Part 5c) Testing the Claim of Difference in Mean Length
```{r Testing Claim w/ Signif. Level}
summary(site1)
sd(site1$Length)
nrow(site1)
summary(site3)
sd(site3$Length)
nrow(site3)
tsum.test(87.75, 29.37401, 1418, 78.59, 24.01731, 2222)
```